Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
Create temporary directories to avoid race condition for the convexhull vertice writeout

  dir.create(paste0(here::here("data"), "/fd_output"), showWarnings = FALSE)

  as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))
}

>>>>

  fs::dir_create(paste0(here::here("data"), "/fd_output"))

  #the convexhull c code creates an output file of vertices, in order to not have multiple threads writing
  #to the same file we have to create individual working directories
  tmp_dir <- paste0(here::here("data", "fd_output", "tmp"), "/tmp_", study, plot_num)
  fs::dir_create(tmp_dir)
  setwd(tmp_dir)

  as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))

  setwd(here::here())
}
